\bf Focusing on Fast Neural Network Inference

### 2018-05-16 wnmt.2018/wnmt.tex
small numerical differences

It is tempting to ignore these consideration, for example, by always decoding with a constant batch and beam size and ignoring hypotheses which are not needed. This is the strategy taken by other inference engines such as Marian, at the cost of lower translation speed due to wasteful processing.

@@

The number of classes in many deep-learning applications is small but this is often not the case with NMT models. For example, ~\citet{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 sub-word units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time-europarl} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We describe the steps to fuse the operations to improve efficiency.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-europarl.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Europarl test set)}
\label{fig:pie-time-europarl}
\end{figure}

@@

Thirdly, the calculation of $max$ and $sum$ can be done in one loop by adjusting $sum$ whenever a higher $max$ is found:
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $\Delta = max_a - max_b$ and $max_b > max_a$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.

>>>>

It is tempting to ignore these considerations, for example, by always decoding with a constant batch and beam size and ignoring hypotheses which are not needed but this comes at a cost of lower translation speed due to wasteful processing.

@@

Most NMT more predict a large number of classes in their output layer, corresponding to the number of words or subword units in their target language. For example, ~\citet{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 sub-word units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time-europarl} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We describe the steps to fuse the operations to improve efficiency.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-europarl.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Europarl test set)}
\label{fig:pie-time-europarl}
\end{figure}

@@

Thirdly, the calculation of $max$ and $sum$ can be accomplished in one loop by adjusting $sum$ whenever a higher $max$ is found:
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $max_a$ is the original maximum value, $max_b$ is the new, higher maximum value, ie. $max_b > max_a$, and $\Delta = max_a - max_b$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.
